Response to the defense feedback

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection{New Implementation}
Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl} also proposes to design and implement clean-slate side-channel free software from scratch.

>>>>

\subsubsection*{New Implementation}
Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch. Researchers~\cite{bernstein2008chacha,langley2016chacha20} also design new cryptographic algorithms (e.g., ChaCha20) that are resilient to cache side-channel attacks.
